---
title: "Homework 7"
author: "Emily Shore"
date: "October 10, 2018"
output: html_document
---

##Random Data Set
```{r}
library(tidyverse)
numbs <- 100
```
####Control jump length before microscope consumption
```{r}
CopejumpC <- rnorm(n=numbs,mean=20,sd=4)
```
####Variable jump length after microplastic consumption
```{r}
CopejumpV <- rnorm(n=numbs,mean=17,sd=4)

ID <- seq_len(numbs)
dataset <- data.frame(ID,CopejumpC,CopejumpV)
print(dataset)
```
#### In choosing sample size, because alot of the copepods we work are very genetically similar, it is important to have a large sample size to try and counteract any lack of genetic variation. Means were determiend by reading a paper of average copepod jump length in mm, and then hypothesizing that the effect of microplastic consumption would have on the mean jump length. The standard deviation was a shot in the dark, becuase I honestly don't know what the effect of microplastic consumption will have on the copepods. 

## ANOVA analysis
```{r}
nControl <- c("Control")
nTreatment <- c("Treatment")

TreatVec <- c(rep(nControl,numbs), rep(nTreatment,numbs))
head(TreatVec)

JumpLength <- c(CopejumpC,CopejumpV)
print(JumpLength)

ANOdata <- data.frame(ID,TreatVec,JumpLength)
head(ANOdata)

ANOmodel <- aov(JumpLength~TreatVec,data=ANOdata)
print(ANOmodel)
summary(ANOmodel)

ANOPlot <- ggplot(data=ANOdata,
                  aes(x=TreatVec,y=JumpLength,
                      fill=TreatVec)) +
  geom_boxplot()
print(ANOPlot)
```

### Running the analysis multiple times changes the P value, but all trials produced a significant P value, changing only slightly. 

## After changing the mean values
```{r}
library(tidyverse)
## Control jump length before microscope consumption
CopejumpC <- rnorm(n=numbs,mean=18,sd=4)

## Variable jump length after microplastic consumption
CopejumpV <- rnorm(n=numbs,mean=16,sd=4)

ID <- seq_len(numbs)
dataset <- data.frame(ID,CopejumpC,CopejumpV)
print(dataset)

## ANOVA analysis
nControl <- c("Control")
nTreatment <- c("Treatment")

TreatVec <- c(rep(nControl,numbs), rep(nTreatment,numbs))
head(TreatVec)

JumpLength <- c(CopejumpC,CopejumpV)
print(JumpLength)

ANOdata <- data.frame(ID,TreatVec,JumpLength)
head(ANOdata)

ANOmodel <- aov(JumpLength~TreatVec,data=ANOdata)
print(ANOmodel)
summary(ANOmodel)

ANOPlot <- ggplot(data=ANOdata,
                  aes(x=TreatVec,y=JumpLength,
                      fill=TreatVec)) +
  geom_boxplot()
print(ANOPlot)
```

### I decreased the mean values for both control and treatment groups, as well as decreased the difference between the two. I found that the P value was extremely less significant than the original means, although it is still statistically significant
```{r}
library(tidyverse)
numbs <- 24

####Control jump length before microscope consumption

CopejumpC <- rnorm(n=numbs,mean=20,sd=4)

####Variable jump length after microplastic consumption

CopejumpV <- rnorm(n=numbs,mean=17,sd=4)

ID <- seq_len(numbs)
dataset <- data.frame(ID,CopejumpC,CopejumpV)
print(dataset)

## ANOVA analysis

nControl <- c("Control")
nTreatment <- c("Treatment")

TreatVec <- c(rep(nControl,numbs), rep(nTreatment,numbs))
head(TreatVec)

JumpLength <- c(CopejumpC,CopejumpV)
print(JumpLength)

ANOdata <- data.frame(ID,TreatVec,JumpLength)
head(ANOdata)

ANOmodel <- aov(JumpLength~TreatVec,data=ANOdata)
print(ANOmodel)
summary(ANOmodel)

ANOPlot <- ggplot(data=ANOdata,
                  aes(x=TreatVec,y=JumpLength,
                      fill=TreatVec)) +
  geom_boxplot()
print(ANOPlot)
```

### With changing the sample size, the minimum sample size required for a significantly significant value was 24 individuals for each of the control and treatment groups. This is a big drop from 100 to 24 individuals. 





























```















