---
title: "homework6"
author: "Emily Shore"
date: "October 3, 2018"
output: html_document
---

z <- rnorm(n=3000,mean=0.2)
z <- data.frame(1:3000,z)

names(z) <- list("ID","myVar")
z <- z[z$myVar>0,]
str(z)
summary(z$myVar)
```{r}
library(tidyverse)
data(iris)
head(iris)

longDat <- iris %>%
  gather(Sepal.Length:Petal.Width, key="Trait"
         ,value="Response") %>%
  arrange(Species)
print(longDat)

speciestrait <- group_by(longDat, Species, Trait)
averages <- summarize(speciestrait, meanSepalLength = mean(Response))
print(averages)

library(ggplot2)
library(MASS)

z <- rnorm(n=3000,mean=0.2)
z <- data.frame(1:3000,z)

names(z) <- list("ID","myVar")
z <- z[z$myVar>0,]
str(z)
summary(z$myVar)

z <- read.table("wolves.csv.csv",header=TRUE,sep=",", stringsAsFactors=FALSE)
str(z)
summary(z)

names(z) <- list("ID","myVar")
z <- z[z$myVar>0,]
str(z)
summary(z$myVar)

p1 <- ggplot(data=z, aes(x=myVar, y=..density..)) +
  geom_histogram(color="grey60",fill="cornsilk",size=0.2) 
print(p1)

p1 <-  p1 +  geom_density(linetype="dotted",size=0.75)
print(p1)

normPars <- fitdistr(z$myVar,"normal")
print(normPars)
str(normPars)
normPars$estimate["mean"] # note structure of getting a named attribute

meanML <- normPars$estimate["mean"] #normal probability density
sdML <- normPars$estimate["sd"]

xval <- seq(0,max(z$myVar),len=length(z$myVar))

 stat <- stat_function(aes(x = xval, y = ..y..), fun = dnorm, colour="red", n = length(z$myVar), args = list(mean = meanML, sd = sdML))
 p1 + stat

expoPars <- fitdistr(z$myVar,"exponential") # exponential 
rateML <- expoPars$estimate["rate"]


stat2 <- stat_function(aes(x = xval, y = ..y..), fun = dexp, colour="blue", n = length(z$myVar), args = list(rate=rateML))
 p1 + stat + stat2

stat3 <- stat_function(aes(x = xval, y = ..y..), fun = dunif,  colour="darkgreen", n = length(z$myVar), args = list(min=min(z$myVar), max=max(z$myVar)))
 p1 + stat + stat2 + stat3 # uniform
#---------------------------------------------------- 
gammaPars <- fitdistr(z$myVar,"gamma") # gamma
shapeML <- gammaPars$estimate["shape"]
rateML <- gammaPars$estimate["rate"]

print(gammaPars)
print(shapeML)
print(rateML)

stat4 <- stat_function(aes(x = xval, y = ..y..), fun = dgamma, colour="brown", n = length(z$myVar), args = list(shape=shapeML, rate=rateML))
 p1 + stat + stat2 + stat3 + stat4 

#--------------------------------------------------------
 # beta
pSpecial <- ggplot(data=z, aes(x=myVar/(max(myVar + 0.1)), y=..density..)) +
  geom_histogram(color="grey60",fill="cornsilk",size=0.2) + 
  xlim(c(0,1)) +
  geom_density(size=0.75,linetype="dotted")

betaPars <- fitdistr(x=z$myVar/max(z$myVar + 0.1),start=list(shape1=1,shape2=2),"beta")
shape1ML <- betaPars$estimate["shape1"]
shape2ML <- betaPars$estimate["shape2"]

statSpecial <- stat_function(aes(x = xval, y = ..y..), fun = dbeta, colour="orchid", n = length(z$myVar), args = list(shape1=shape1ML,shape2=shape2ML))
pSpecial + statSpecial

#------------------------------------------------
```{r}
z <- read.table("wolves.csv.csv",header=TRUE,sep=",", stringsAsFactors=FALSE)
str(z)
summary(z)

#-------------------------------------------------------
# Simmulate new data based on best fitting distribution
set.seed(3)
wolves <- rgamma(24, 4.5492708, rate=1.1492894,)
wolves1 <- data.frame(1:24, wolves)
names(wolves1) <- list("ID","myVar")
p2 <- ggplot(data=wolves1, aes(x=myVar, y=..density..)) +
  geom_histogram(color="grey60",fill="cornsilk",size=0.2) 
print(wolves1)
p2 <-  p2 +  geom_density(linetype="dotted",size=0.75)
print(p2)

# This is the original data 

p1 

# How do the two histogram profiles compare? Do you think the model is doing a good job of simulating realistic data that match your original measurements? Why or why not?
#- The two histograms are pretty similar, with having the same general curve of the data. The model is doing a good job of simulating realistic data to match the original measurements, and this is because the graphs have similar densities exhibited by the y axis values, as well as individuals represented in the graph. 



```













